### 2023-04-28 chapter2/chapter2.tex
Moved heatmap figure into results
Tweaked some wording in last results paragraph

The resulting heatmap reveals patterns of similar signatures interspersed among a high background of noise (Fig.~\ref{fig:hierarchy}). However, we identify at least 12 clusters with a strong and consistent patterns of constraint, with many having significant associations with certain processes, functions, or compartments. For example, cluster X is strongly enriched in Y, and cluster A contains many proteins involved in B. Though these preliminary results suggest the existence of high-level relationships between certain patterns of conserved features and function, additional insights into the biophysical and mechanistic details that underpin these associations will depend on more in-depth analyses of specific clusters and the properties of their constituent IDRs.

>>>>

The resulting heatmap reveals patterns of similar signatures interspersed among a high background of noise (Fig.~\ref{fig:hierarchy}). However, we identify at least 12 clusters with a strong and consistent patterns of constraint, with many having significant associations with certain processes, functions, or compartments. For example, cluster X is strongly enriched in Y, and cluster A contains many proteins involved in B. Though these preliminary results suggest the existence of high-level relationships between certain patterns of conserved features and function, further insight into the biophysical and mechanistic details that underpin these associations will rely on more in-depth analyses of specific clusters and the properties of their constituent IDRs.
